---
title: "Exploring Supreme Court data I.1"
output: html_notebook
---

```{r}
library(tidyverse)
load("data/supreme-court-1-1.Rdata")
```

```{r}
sup_court <- SCDB_2019_01_caseCentered_Citation
```

```{r}
colnames(sup_court)
```

Right now, we are interested in decisions.

```{r}
sup_court %>%
    head() %>%
    select(contains('decision'))
```

This is not what we need.

```{r}
sup_court
```

As an example, the full opinion to 'Cleveland v. United States' can be found ![here](https://www.courtlistener.com/opinion/104324/cleveland-v-united-states/). We will therefore begin by trying to crawl this website.

A crawler in R is given by the package ![RCrawler](https://github.com/salimk/Rcrawler).

```{r}
library(Rcrawler)
ex_link <- 'https://www.courtlistener.com/opinion/104324/cleveland-v-united-states/'
extracted_decision <- LinkExtractor(ex_link)
extracted_decision %>% names()
```

```{r}
extracted_decision$Info %>% names()
```

```{r}
decision_info <- extracted_decision$Info
decision_page <- decision_info$Source_page
```

The decision page consists of the entire html document. We therefore need some way of simplifying this document.

**Intermediate** 40 minutes.

